---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(fs)

cat_tree <- function(x, ...) {
  t <-  capture.output(dir_tree(x, ... = ...))
  t[[2]] <- paste0(" ", t[[2]])
  cat(purrr::map_chr(t[2:length(t)], ~ paste0(.x, "\n")))  
}

temp_dir <- tempdir()
dir_site <- path(temp_dir, "my_site")
if(dir_exists(dir_site)) unlink(dir_site, recursive = TRUE, force = TRUE)
dir_create(dir_site)   

file_utils <- system.file("readme_files", package = "ecodown")
lapply(dir_ls(file_utils), function(x) file_copy(x, dir_site, overwrite = TRUE))
```

# ecodown

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/edgararuiz/ecodown/branch/main/graph/badge.svg)](https://app.codecov.io/gh/edgararuiz/ecodown?branch=main)
[![R-CMD-check](https://github.com/edgararuiz/ecodown/workflows/R-CMD-check/badge.svg)](https://github.com/edgararuiz/ecodown/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ecodown)](https://CRAN.R-project.org/package=ecodown)
<!-- badges: end -->

The goal of `ecodown` is to make it possible for your R package's documentation to
be published in a Quarto site.  

The vision for `ecodown` is that it is used to document a group of related packages
that will be published to a single Quarto site.  

## Installation

You can install the development version of `ecodown` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("edgararuiz/ecodown")
```

## Using 

```{r}
library(ecodown)
```
 
## Clone the repo

```{r}
mleap_location <- ecodown_clone("https://github.com/rstudio/mleap")
```

## Convert and move to Quarto folder

```{r, eval = FALSE}
ecodown_convert(mleap_location, quarto_sub_folder = "mleap")
```

```{r, echo = FALSE}
ecodown_convert(mleap_location, quarto_folder = dir_site, quarto_sub_folder = "mleap")
```

## Render site

```{r, eval = FALSE}
ecodown_quarto_render()
```

```{r, echo = FALSE}
ecodown_quarto_render(dir_site)
```
## Autolink

```{r, eval = FALSE}
ecodown_autolink()
```

```{r, echo = FALSE}
ecodown_autolink(dir_site)
```








 
 
 