---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(fs)

cat_tree <- function(x, ...) {
  t <-  capture.output(dir_tree(x, ... = ...))
  t[[2]] <- paste0(" ", t[[2]])
  cat(purrr::map_chr(t[2:length(t)], ~ paste0(.x, "\n")))  
}

temp_dir <- tempdir()

if(dir_exists(path(temp_dir, "mleap"))) dir_delete(path(temp_dir, "mleap"))
if(dir_exists(path(temp_dir, "mleap_site"))) dir_delete(path(temp_dir, "mleap_site"))
```

# ecodown

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/edgararuiz/ecodown/branch/main/graph/badge.svg)](https://app.codecov.io/gh/edgararuiz/ecodown?branch=main)
<!-- badges: end -->

The goal of `ecodown` is to help convert package documentation to Quarto.  The main idea is to use `ecodown` to document multiple packages in a single 
Quarto site. 

## Installation

You can install the development version of ecodown from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("edgararuiz/ecodown")
```

## Example

```{r}
library(ecodown)
```
 
### Clone the package's repo

`ecodown` uses the package's source to produce the documentation. Use 
`package_clone_git_repo()` to download the the package.  By default, it clones 
the repo to a temp directory. We will use the `mleap` package for this example:
 
```{r}
mleap_location <- package_clone_git_repo("https://github.com/rstudio/mleap")
```

Here are the current contents of the package:

```{r, echo = FALSE}
cat_tree(mleap_location, recurse = FALSE)
```

And the contents of the 'man' folder: 

```{r, echo = FALSE}
cat_tree(path(mleap_location, "man"))
```

### Build the documentation

`package_build_documentation()` is the main function out of `ecodown`. It is 
similar to the `pkgdown`'s `build_site()`.  It will map and copy the README, 
NEWS and vignettes files. It will also parse and convert the '.Rd' files into 
'.Md' files.  

The `project_folder` creates a sub-folder in your workspace where the documentation
is going to be converted and copied to.

```{r, eval = FALSE}
package_build_documentation(
  pkg_folder = mleap_location,
  project_folder = "mleap"
)
```

```{r, echo = FALSE}
temp_dir <- tempdir()

package_build_documentation(
  pkg_folder = mleap_location,
  root_folder = path(temp_dir, "mleap_site"),
  project_folder = "mleap"
)
```

This will be the contents of the new 'mleap' sub-folder.

```{r, echo = FALSE}
cat_tree(path(temp_dir, "mleap_site/mleap"))
```

