---
title: "Build site manually"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{manual_steps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(fs)

cat_tree <- function(x, ...) {
  t <-  capture.output(dir_tree(x, ... = ...))
  t[[2]] <- paste0(" ", t[[2]])
  cat(purrr::map_chr(t[2:length(t)], ~ paste0(.x, "\n")))  
}

temp_dir <- tempdir()
dir_site <- path(temp_dir, "test_site")
if(dir_exists(dir_site)) unlink(dir_site, recursive = TRUE, force = TRUE)
dir_create(dir_site)   

file_utils <- system.file("testutils/quarto_files", package = "ecodown")
lapply(dir_ls(file_utils), function(x) file_copy(x, dir_site, overwrite = TRUE))
```

In general, there are 4 steps to keep the documents up-to-date in Quarto:

1. [Prepare the documentation for Quarto](#prepare-the-documentation-for-quarto)
1. [Run Quarto locally](#run-quarto-locally)
1. [Run auto-linking](#run-auto-linking)
1. Commit the changes back to the site

The `site_build_quarto()` function will run the first three steps. The steps 
described in this article is for those who may need to have more fine grain 
control on how and when to build parts of the site.

```{r}
library(ecodown)
```
 
### Prepare the documentation for Quarto

`package_build_documentation()` is the main function out of `ecodown`. It is 
similar to the `pkgdown`'s `build_site()`.  It will map and copy the README, 
NEWS and vignettes files. It will also parse and convert the **.Rd** files into 
**.Md** files.  

The `quarto_sub_folder` creates a sub-folder in your workspace where the 
documentation is going to be converted and copied to.

```{r, eval = FALSE}
package_clone_and_build("https://github.com/rstudio/mleap")
```

```{r, echo = FALSE}
package_clone_and_build(
  "https://github.com/rstudio/mleap",
  quarto_base_folder = dir_site
)
```
## Run Quarto locally

Use `quarto::quarto_render()` to convert the markdown files into HTML. 

For this example, an 'index.md' and a '_quarto.yml' file to make it possible to 
run Quarto properly.  This particular setup file points Quarto to a **docs** 
sub-folder.

```{r, eval = FALSE}
quarto::quarto_render()
```

```{r, include = FALSE}
quarto::quarto_render(dir_site)
```

This the content of the **docs** sub-folder after the process completes:

```{r, echo = FALSE}
top_lines <- capture.output(cat_tree(path(dir_site, "docs")))[1:14]
resume_cat <- c(top_lines, " ... more files ...")
cat(paste0(resume_cat, collapse = "\n") )
```

## Run auto-linking

Auto-linking here refers to converting written function names in a given HTML
to links to the reference of that function.  It uses the package `downlit` to 
accomplish this.

In the background, `package_build_documentation()` not only builds the documentation
in a format Quarto accepts, but also pre-loads the necessary R `options` so that
`downlit` is aware that your package is inside your Quarto site.  This will enable
`downlit` to link references of your package to your Quarto site, instead of 
creating a generic link. 

Use the `site_autolink_html()` function to perform the auto-link over all of the
Quarto site, or a sub-folder in it.  By default, it looks at the `output-dir` entry
in the _quarto.yml file to find the location of the HTML files created by
Quarto.

```{r, include = FALSE}
site_autolink_html(path(dir_site, "docs"))
```

```{r, eval = FALSE}
site_autolink_html()
```


```{r, echo = FALSE}
site_autolink_html(path(dir_site, "docs"))
```

